---
title: "data cleaning"
author: "Shuchen"
date: "2022-11-06"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(rvest)
library(fuzzyjoin)
library(formattable)
```
```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(rvest)
library(fuzzyjoin)
library(formattable)
```



```{r}
car <-read.csv('CarRentalData.csv')
car <- na.omit(car)
car <- car[-c(5,6,7,8,9,10,11)]
car$fuelType <- as.factor(car$fuelType)
car$vehicle.model <- paste(car$vehicle.make,car$vehicle.model)
car <- car[-c(5)]
car$vehicle.model <- as.factor(car$vehicle.model)
car <- car[car$fuelType %in% c("GASOLINE", "HYBRID","DIESEL"), ]
car <- car[car$vehicle.type %in% c("suv", "car"),]
car <- car %>% filter(reviewCount >= 20) #mean review count 31.11944
car <- car %>% group_by(vehicle.model) %>% filter(n()>5) #more than 5 reviews
View(car)
```

```{r}
#Model Preference with its weighted rating 
ModelPreference <- car%>%group_by(vehicle.model)%>%summarise(weighted.mean(rating,renterTripsTaken))
colnames(ModelPreference)<-c("Model","WeightedAverageRating")
ModelPreference$WeightedAverageRating<-as.numeric(formatC(ModelPreference$WeightedAverageRating, digits = 4, format = "f"))

```

```{r} 
#getting top X models
ModelPreference <- ModelPreference %>% arrange(desc(WeightedAverageRating))
ModelPreference_top10 <-head(ModelPreference,10)
ModelPreference_top10
```

#getting cleaned csv
#write.csv(ModelPreference,"ModelPreference.csv", row.names = FALSE)
#write.csv(ModelPreference_top10,"ModelPreference_top10.csv", row.names = FALSE)
```{r}
#Kia Sorento (ILS 117,266)
kiasorento <- read_html("https://motowheeler.com/il/hybrid-cars/kia-sorento-plug-in-hybrid-sx-awd-2023-8946")
kiasorento <- kiasorento %>% html_nodes("body") %>% html_table()
kiasorento <- as.data.frame(kiasorento)

#Jaguar F Type is not yet found in israel (coming soon)

#Chevrolet Corvette Stingray (ILS 210,105)
corvette<- read_html("https://motowheeler.com/il/cars/chevrolet-corvette-stingray-1lt-coupe-1098")
corvette <- corvette %>% html_nodes("body") %>% html_table()
corvette <- as.data.frame(corvette)

#MINI Cooper Countryman (ILS 100,395)
countryman <- read_html("https://motowheeler.com/il/cars/mini-cooper-countryman-2022-3464")
countryman <- countryman %>% html_nodes("body") %>% html_table()
countryman <- as.data.frame(countryman)

#Subaru Outback (ILS 92,960)
outback <- read_html("https://motowheeler.com/il/cars/subaru-outback-base-1556")
outback <- outback %>% html_nodes("body") %>% html_table()
outback <- as.data.frame(outback)

#Porsche 911 (ILS 349,140)
porsche <- read_html("https://motowheeler.com/il/cars/porsche-911-carrere-car-8239")
porsche <- porsche %>% html_nodes("body") %>% html_table()
porsche <- as.data.frame(porsche)

#Mercedes C class
C.class <- read_html("https://motowheeler.com/il/cars/mercedes-benz-c300-cabriolet-2023-6317")
C.class <- C.class %>% html_nodes("body") %>% html_table()
C.class <- as.data.frame(C.class)

#Mini Cooper (ILS79,005)
mini <- read_html("https://motowheeler.com/il/cars/mini-cooper-hardtop-2-door-2022-3592")
mini <- mini %>% html_nodes("body") %>% html_table()
mini <- as.data.frame(mini)

#Jeep Wrangler JK (ILS 115,903)
JK <- read_html("https://motowheeler.com/il/cars/jeep-wrangler-unlimited-willys-2022-5158")
JK <- JK %>% html_nodes("body") %>% html_table()
JK <- as.data.frame(JK)
```
# As the datasets in the original websites, the details for car models are too messy and cannot be cleaned and organized in R (messy structure and lack of data, etc.). We directly extract the csv files and clean them manually to generate those tables in the fleet recommendation tab.
```{r}
write.csv(kiasorento,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/kiasorento.csv",row.names = FALSE)
write.csv(corvette,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/corvette.csv",row.names = FALSE)
write.csv(countryman,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/countryman.csv",row.names = FALSE)
write.csv(outback,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/outback.csv",row.names = FALSE)
write.csv(porsche,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/porsche.csv",row.names = FALSE)
write.csv(C.class,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/C.class.csv",row.names = FALSE)
write.csv(mini,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/mini.csv",row.names = FALSE)
write.csv(JK,"/Users/elianasong/Desktop/y3s1/DBA3702/Project/is data source/JK.csv",row.names = FALSE)
```